%ReferenceList

\begin{parcolumns}[colwidths={1=2.5 cm, 2=12 cm}]{2}

%Subsections
\colchunk{\\
\textbf{Pumped\\Storage\\Hydropower}
\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
\textbf{Vehicle to Grid}
<<<<<<< HEAD
\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ 
\textbf{Power-to-Gas}
=======
\\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
\textbf{Hydrogen Storage Technology}
>>>>>>> 65b63a9696a72157cd4aff3c88be2bb5c2c597d9
}

%Reference List
\colchunk{\\
1. \url{https://en.wikipedia.org/wiki/Pumped-storage_hydroelectricity} \\
2. \url{https://www.bdew.de/presse/presseinformationen/zahl-der-woche-gut-32-mrd-kilowattstunden/} \\
3. \url{https://www.hydropower.org/country-profiles/germany} \\
4. \url{https://www.energy.gov/sites/prod/files/2019/07/f65/Storage\%20Cost\%20and\%20Performance\%20Characterization\%20Report_Final.pdf} \\
5. Kamath \url{https://www.tep.com/wp-content/uploads/2016/04/12-TEP_UNSE-2017-IRP-Workshop-Energy-Storage-EPRI.pdf} \\
6. May G, A Davidson, and B Monahov. 2018. “Lead batteries for utility energy storage: A review.” Journal of Energy Storage 15(2018):145-157. \\
7. \url{https://www.lazard.com/media/438042/lazard-levelized-cost-of-storage-v20.pdf} \\
8. \url{https://en.wikipedia.org/wiki/Darcy\%E2\%80\%93Weisbach_equation} \\
9. \url{https://books.google.co.uk/books?id=TPReBwAAQBAJ&lpg=PA25&dq=info\%3A1fSw0yVikpMJ\%3Ascholar.google.com&lr&pg=PA25#v=onepage&q&f=false} \\
10. \url{https://phys.org/news/2016-10-pumped-storage-hydroelectricity.html} \\
11. \url{https://www.ifc.org/wps/wcm/connect/79ad4356-6f18-4955-bf35-adcd6d072897/GPN_EHSHydropower.pdf?MOD=AJPERES&CVID=mR5BwAV} \\
12. \url{https://en.wikipedia.org/wiki/Wind_power_in_Germany} \\
\\
1. \url{https://en.wikipedia.org/wiki/Vehicle-to-grid} \\
2. \url{https://www.isi.fraunhofer.de/content/dam/isi/dokumente/sustainability-innovation/2010/WP4-2010_V2G-Valuation.pdf} \\
3. \url{https://www.erneuerbar-mobil.de/sites/default/files/publications/anhang-optum-ap6_1.pdf} \\
4. \url{https://www.bdew.de/presse/presseinformationen/zahl-der-woche-gut-32-mrd-kilowattstunden/} \\
5. \url{https://www.kba.de/DE/Statistik/Fahrzeuge/Bestand/b_jahresbilanz.html} \\
6. \url{https://www.isi.fraunhofer.de/content/dam/isi/dokumente/sustainability-innovation/2010/WP4-2010_V2G-Valuation.pdf} \\
7. \url{https://de.statista.com/statistik/daten/studie/460234/umfrage/ladestationen-fuer-elektroautos-in-deutschland-monatlich/} \\
8. \url{https://www.volkswagenag.com/presence/konzern/group-fleet/dokumente/Compendium_Electric_charging_for_fleets_DE.pdf} \\
9. \url{https://en.wikipedia.org/wiki/Tesla_Supercharger} \\
10. \url{https://backend.orbit.dtu.dk/ws/portalfiles/portal/137328554/efficiency_paper.pdf} \\
11. \url{https://www.bmwi.de/Redaktion/DE/Downloads/V/verordnung-ladeeinrichtungen-elektromobile-kabinettbeschluss.pdf?__blob=publicationFile&v=3} \\
\\
<<<<<<< HEAD
1. \url{https://en.wikipedia.org/wiki/Wind_power}\\
2. \url{https://en.wikipedia.org/wiki/Power-to-gas}\\
3. \url{https://www.bdew.de/presse/presseinformationen/zahl-der-\\woche-gut-32-mrd-kilowattstunden} \\
4. \url{https://www.journals.elsevier.com/international-journal-\\of-hydrogen-energy}\\
5. \url{https://www.dena.de}\\
6. \url{https://www.sciencedirect.com/science/article/pii/S\\0306261918315319}\\
7. \url{https://en.wikipedia.org/wiki/Power-to-gas\#Efficiency}\\ 
8. \url{https://www.sciencedirect.com/topics/engineering/alkaline-\\water-electrolysis}\\
9. \url{https://en.wikipedia.org/wiki/Polymer\_ electrolyte\_ membrane\_ electrolysis\# PEM\_ Efficiency}\\
10. \url{https://www.oxfordenergy.org/wpcms/wp-content/uploads/2018/10/Power-to-Gas-Linking-Electricity-and-Gas-in-a-\\Decarbonising-World-Insight-39.pdf}\\
11. \url{https://de.wikipedia.org/wiki/Power-to-Gas\# Wasserstoff\\einspeisung\_ versus\_ Methanisierung}\\
12. \url{http://epub.sub.uni-hamburg.de/epub/volltexte/2014/35363/pdf/Masterthesis\_Bastian\_Hey
\_Power\_to\_Gas.pdf}\\
13. \url{https://en.wikipedia.org/\\wiki/Electrolysis\_of\_water 
\#Equations}\\
14. \url{https://en.wikipedia.org/wiki/Sabatier\_reaction}\\
=======
1. \url{https://www.researchgate.net/publication{336527927_Hydrogen_Energy_Storage}} \\
2. \url{https://en.wikipedia.org/wiki/Grid_energy_storage#Hydrogen} \\
3. \url{https://www.irena.org/-/media/Files/IRENA/Agency/Publication/2018/Sep/IRENA_Hydrogen_from_renewable_power_2018.pdf} \\
4. \url{https://www.azocleantech.com/article.aspx?ArticleID=29} \\
5. \url{https://en.wikipedia.org/wiki/Grid_energy_storage#Hydrogen} \\
6. \url{https://www.hydrogenics.com/technology-resources/hydrogen-technology/fuel-cells/} \\
7. \url{https://www.nrel.gov/docs/fy10osti/48360.pdf} \\
8. \url{https://bit.ly/364Wv1p} \\
9. \url{https://en.wikipedia.org/wiki/Combined_cycle_power_plant} \\
>>>>>>> 65b63a9696a72157cd4aff3c88be2bb5c2c597d9
}

\end{parcolumns}
\clearpage